Uncertain Effects of DFT Functionals on Charge Dynamic of Organic Semiconductor

### 2024-10-10 paper.tex
update

\section{Introduction}

@@

The first challenge relates to the Born-Oppenheimer approximation in quantum
mechanics, which simplifies the problem by separating the electronic and nuclear
coordinates. As a result, the time evolution of the atomic coordinates can be modeled by solving the Newton's equation using empirical force field to approximate the potential energy surfaces (need citation).

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
    \caption{The multiscale model workflow for OSC. Step 1: MD simulation to generate atom coordinates. Step 2: Molecule energy $E_i$ calculation. Step 3: Calculation of Reorganization energy $\lambda_{i,j}$ and coupling element $J_{i,j}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$. Step 4: Modelling dynamics on device level, such as ToF calculation.}
    \label{fig:MSM}
\end{figure}

In overcoming the challenges and achieving the multiscale model, uncertainties are introduced.

While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the atomic coordinates are not exactly the same as that modeled by the many-electron schr\"{o}dinger equation.
So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
This is one source of uncertainty that have not been investigated.
But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty.

Secondly, state localization is not exactly a time dependent DFT process. 
But for amorphous OSCs, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.

Lastly, the exchange-correlation functional in DFT do not have explicit formula and common practice is to use empirical functional, whose suitability is usually unknown for most molecules.

The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional in DFT will bring uncertainties to the multiscale model. 
The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model.

@@

Most literature report the charge mobility in a steady state setting, where no electrodes are used and the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions. 
Over a long time period, the charge occupation on each molecule $\pi_i$ reach equilibrium, and the steady state diffusive velocity is calculated via:
\begin{equation}
    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} \vec{r}_{ij} = \mathbb{E}f(M_{\infty})
\end{equation} 
Specifically, the focus will be placed on following questions: 
\begin{itemize}
    \item How do DFT functionals change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
    \item How do DFT functionals change the charge mobility?
    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution?
    \item Can we estimate the range of the quantity of interest, given a confidence level?
\end{itemize}

Calculation of $v_\text{ToF}$ or $v_\text{SS}$ commonly use kinetic Monte Carlo (KMC) to obtain multiple realizations of full charge dynamic trajectories 
or numerically solving the master equation. 
However, those two commonly used methods are not suitable for quantifying the uncertainty effect of multiscale model charge dynamics for the following reasons.

Firstly, KMC produces random variables whose expectation is the charge mobility. The prior knowledge of the random variable distribution as well as the required KMC samples to achieve converged expectation is unknown. So this method itself pose further challenge for our uncertainty quantification. 
Secondly, the numerical solution of the master equation has stability and convergence issue, that is, a small integration time step is required to achieve stability and a long computational time to achieve convergence result. These aspects add additional difficulty for uncertainty quantification.

{\huge Here}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multiscale Model}
\label{sec:MSM}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
    \caption{The multiscale model workflow for OSC. Step 1: MD simulation to generate atom coordinates. Step 2: Molecule energy $E_i$ calculation. Step 3: Calculation of Reorganization energy $\lambda_{i,j}$ and coupling element $J_{i,j}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$. Step 4: Modelling dynamics on device level, such as ToF calculation.}
    \label{fig:MSM}
\end{figure}

Figure \ref{fig:scatterE} shows the workflow of the multiscale model for ToF calculation. In brief summary, the process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates from which the vertex and edge sets are defined.
Specifically, using a cutoff distance $r_\text{cutoff}$, any two molecules whose center of mass (COM) within $r_\text{cutoff}=0.5$ [nm] form a pair of molecules where directed edge weight can be calculated.
Secondly, quantum electronic structure calculation is performed to obtain the electronic structure properties: The molecule energy $E_i$ of molecule $i$, the reorganization energy between $\left\{\lambda_{i,j}\right\}$ and coupling element $\left\{\Delta J_{i,j}\right\}$ between the pair of molecules $i$ and $j$. All in unit of eV.

Then, those electronic structure properties are used to calculate the bi-molecular Marcus rate between the molecules:
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{i,j}|^2}{\sqrt{4\pi \lambda_{i,j} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{i,j} + q \vec{F} \cdot \vec{r}_{i,j} - \lambda_{i,j})^2}{4\lambda_{i,j} k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant, $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), external electric field $\vec{F}$ and the charge of the carrier $q$ (in \unit[]{e}) can be considered as parameters of the simulation. The vector $\vec{r}_{i,j} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses of molecules $i$ and $j$, which is calculated using cyclic boundary conditions depending on system setting. And $\Delta E_{i,j} = E_i - E_j$ is the energy difference between a pair of molecules.
Finally, the quantity of interest, such as ToF $\tau$, can be calculated from the transition rates $\omega_{ij}$.

\subsection{Molecule Dynamics Simulation}
In a material system of $N_a$ atoms with mass and position denoted by $m_i$ and $\vec{r}_i$ respectively, molecular dynamics (MD) models the evolution of the atomic coordinate using Newton's second law, which is written in Hamilton equation: 
\begin{equation}
    \begin{cases}
        \frac{d \vec{r}_i}{dt} = \frac{\partial H }{\partial \vec{p}_i} \\
        \frac{d \vec{p}_i}{dt} = -\frac{\partial H }{\partial \vec{r}_i}
    \end{cases}
    \label{eq:Hamilton}
\end{equation}
for $i=1,\cdots,N_a$, where the Hamiltonian $H$ reads:
\begin{equation}
    H=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})
    \label{eq:Hamilton2}
\end{equation}

@@

\subsection{Electronic Structure Calculation} 
The molecule energy $E_i$ in the multiscale model is calculated as:
\begin{equation}
E_i = (U^\text{cC}_i - U^\text{nN}_i) + (E^\text{c}_i - E^\text{n}_i)
\label{eq:E_i}
\end{equation}
where $U^\text{cC}_i$ is the internal energy of charged molecule $i$ in the optimized charged geometry, and $U^\text{nN}_i$ is the internal energy of neutral molecule $i$ in the optimized neutral geometry. The calculation of $U$ and how to obtain optimized geometry will be introduced in the subsection DFT Calculation.
In the superscript the lowercase letter "c/n" represents the molecule state of being charged/neutral and uppercase letter "C/N" represents the geometry of the charged/neutral molecule. This notation also applies for $E^\text{c}_i$, $E^\text{n}_i$. 
And $E^\text{n}_i = E^\text{n,el}_i + E^\text{n,induce}_i$ is the energy due to the electrostatic and induced dipole moment effect. Compared with the electrostatic energy calculated using the dielectric constant, this energy in multiscale model is very sensitive to the molecule structure, making the uncertainty quantification of charge transport in multiscale model much more important. 
A precise method for calculating $E^\text{n}_i$ is to use the Thole Model as detailed in \cite{Baumeier2011}.

This method has the steps include: first, each atom $a_i$ is initialized with charges $q_{a_i}$ and dipole moment $D_{a_i}$. 
Then the induced dipoles of each atom are calculated using the electric field generated by other atoms $b_j$.
This calculation continuous iteratively to update the induced dipoles of every atom by considering the fields due to other dipoles.
Finally, it checks for convergence, if the induced dipoles have not changed significantly from one iteration to the next, the iterative process stops.
Finally, the electrostatic energy and polarization energy using the final set of induced dipoles and atomic charges. So in summary, $E^\text{n}_i$ is a function of all atoms' charges and induced dipoles: $E^\text{n}_i = \sum\limits_{a_i} f(q_{a_i}, D_{a_i})$.

The reorganization energy $\lambda_{i,j}$ between molecule $i$ to molecule $j$ is given as:
\begin{equation}
    \lambda_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
\end{equation}

%%%%%%%
The coupling element $J_{i,j}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
\begin{equation}
    J_{i,j} = \frac{ J^0_{i,j}- \frac{1}{2}(e_i+e_j)S_{i,j} }{ 1- S_{i,j}^2 }
    \label{equ:JAB}
\end{equation}
where $J^0_{i,j} = \langle \psi^i | \hat{H} | \psi^j \rangle $, $e_i = \langle \psi^i | \hat{H} | \psi^i \rangle $, $e_j = \langle \psi^j | \hat{H} | \psi^j \rangle $, and $S_{i,j}=\langle \psi^i | \psi^j \rangle $ with bra-ket notation, $\hat{H}$ is the Hamiltonian of the electron wave function, and $\psi^{i,(j)}$ is the electron wave function of molecule $i(j)$. A single molecule is called a monomer, and a pair of two molecules is called a dimer.

Denote $\psi^\text{D}$ as the electron wave function of the two molecules,  $J^0_{i,j}$ can be calculated via:
$
    J^0_{i,j} = \mathbf{\gamma}^i \text{diag}(\mathcal{E}) \mathbf{\gamma}^j
$, 
where $\mathbf{\gamma}^i = \langle \psi^i | \psi^\text{D} \rangle$ and $\mathbf{\gamma}^j = \langle \psi^j | \psi^\text{D} \rangle$ are called the projections of the monomer orbitals $\psi^i, \psi^j$ on the dimer orbitals $\psi^\text{D}$. And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting of energy eigenvalues of the one-particle wave function of the dimer.

In conclusion, the calculation of electronic structure relies on the internal energy and electron wave function. As mentioned in the introduction, DFT is used to calculate these two quantities. The next subsection will introduce the details of DFT.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{DFT Calculation}
In multiscale model, each molecule is an $N_\text{el}$-electron system, and the probability of finding electrons in space is described by the wavefunction.
In DFT, the internal energy calculated from the Kohn–Sham equation \cite{kohn_self_1965} reads:

\begin{equation}
    U^\text{KS}[\rho] = T_s[\rho] + \int \hat{V}_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]
    \label{eq:KS_model}
\end{equation}
where the electron density is $\rho=\sum\limits_{i=1}^{N_\text{el}} \phi_i^\star(\vec{r}) \phi_i(\vec{r})$, $T_s[\rho]$ is the kinetic energy depending on $\rho$,  $\hat{V}_\text{ext}$ is the external potential energy,  $\hat{V}_\text{H}[\rho]$ is the Hartree energy accounting for the Coulomb interaction, $\hat{V}_\text{XC}[\rho]$ is the exchange-correlation energy accounting for the difference between classical and quantum effect. The exact form of $\hat{V}_\text{XC}[\rho]$ is not known, in practice, this energy term is approximated by DFT functionals. In our work, ten DFT functionals are used to represent this energy term. 
The single-electron wave function $\phi_i$ satisfies: 
\begin{equation}
    (-\frac{1}{2}\nabla^2_{\vec{r}} + \hat{V}_\text{ext} + \frac{\delta \hat{V}_\text{H}[\rho]}{\delta \rho} + \frac{\hat{V}_\text{XC}[\rho]}{\delta \rho}) \phi_i^\text{KS}(\vec{r}) =  \epsilon^\text{KS}_i[\rho] \phi^\text{KS}_i (\vec{r}) 
    \label{eq:KS2}
\end{equation}
with $\epsilon^\text{KS}_i[\rho]$ being the energy eigenvalue of electron $i$. 
In practice, Equation \ref{eq:KS2} is solved iteratively, and the wave function is represented by a linear combination of basis functions call basic sets. 
In this work, the basic set def2-tzvp \cite{weigend_accurate_2006} is used. The DFT computation is performed by VOTCA \cite{Baumeier2011} which internally calls ORCA software.
The internal energy $U^\text{KS}$ depends on the atomic coordinates of the molecule. The optimized geometry of a molecule refers to the atomic coordinates that minimize $U^\text{KS}$.

\section{Time-of-flight Calculation}
The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the edge weights $\omega_{i,j}$ represent the Marcus rate from molecule $i$ to molecule $j$. The charge dynamics are modeled as a continuous-time random walk on this graph. In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.

As mentioned in the introduction, a quantity of interest in modeling charge dynamics is the ToF, which is the time for charges carriers injected into the Source to be detected at the Sink.
A typical method to obtain the ToF is to use the kinetic Monte Carlo (KMC) method to simulate the CTRW for many times and record ToFs, which are random variables. 
To be detailed: 
But a challenge with this KMC is that one need to repeat a large number $N_\text{KMC}$ of KMC simulation to guarantee an converged ToF. Furthermore, $N_\text{KMC}$ is not known before running KMC, posing a great challenge to quantify the uncertainty of ToF from the multiscale model. 
An alternative method to overcome the convergence challenge is to obtain ToF as the hitting time a continuous time Markov chain.

Due to Pauli repulsion, each node can be occupied by at most one charge carrier. For a system with $N$ molecules and $N_c$ charge carriers, there are ${N \choose N_c}$ possible occupation states. Each occupation state is denoted as $\mathbf{s}$. A state is called the Source state if all carriers occupy the Source nodes, and a Sink state if at least one of the Sink nodes is occupied.

The transition rates between the states can be obtained from the adjacency matrix $\mathbf{W}:\omega_{i,j}$, since the connectivity of states is encoded in the connectivity of the nodes, as detailed in ~\cite{chen_graph_2024}. 
According to such connectivity, 
the transition rates $\Omega_{\mathbf{s} \mathbf{s}' }$ from state $\mathbf{s}$ to $\mathbf{s}'$ is:
\begin{equation}\label{eq:transition_rates}
	\Omega_{\mathbf{s} \mathbf{s}^\prime} =
	\begin{cases}
	     0			&  \mathbf{s} \text{ is not connected to } \mathbf{s}^\prime,\\
	    \omega_{ij}	&  \mathbf{s} \text{ is connected to } \mathbf{s}^\prime \text{ due to } (i,j)
	\end{cases}
\end{equation}

Then the transition probability from state $\mathbf{s}$ to $\mathbf{s}'$ is $p_{\mathbf{s} \mathbf{s}^\prime} = \Omega_{\mathbf{s} \mathbf{s}^\prime}/D_\mathbf{s}$ where $D_\mathbf{s} := \sum_{\mathbf{s}^\prime \ne \mathbf{s}} \Omega_{\mathbf{s} \mathbf{s}^\prime}$.
And the expected time from state $\mathbf{s}$ to reach the Sink state $\tau_\mathbf{s}$ is calculated via: 
\begin{equation}\label{eq:hitting_time}
	\tau_\mathbf{s} = \begin{cases}
		\frac{1}{D_\mathbf{s}} + \sum_{\mathbf{s}^\prime \ne \mathbf{s}} p_{\mathbf{s} \mathbf{s}^\prime} \tau_{\mathbf{s}^\prime} &\text{if $\mathbf{s}$ is not a sink state},\\
		0 &\text{else.} 
	\end{cases}
\end{equation}

To account for all possible starting nodes of the carriers, all Source states must be considered. The random walk process can be modeled as a parallel electric network of capacitors \cite{doyle_random_2000}. Accordingly, the ToF is evaluated using the harmonic mean:
\begin{equation} 
\tau = N_\text{source} \left[\sum_{\mathbf{s} \in \text{Source}} (\tau_\mathbf{s}^\ast)^{-1}\right]^{-1},
\label{eq:ToF}
\end{equation}
where $N_\text{source}$ is the number of Source states.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results on BCP}
\label{sec:result}

>>>>

\section{Background}

@@

The first challenge relates to the Born-Oppenheimer approximation in quantum
mechanics, which simplifies the problem by separating the electronic and nuclear
coordinates. As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces (need citation).

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
    \caption{The multiscale model workflow for OSC. Step 1: MD simulation to generate atom coordinates. Step 2: Molecule energy $E_i$ calculation. Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$. Step 4: Modelling dynamics on device level, such as ToF calculation.}
    \label{fig:MSM}
\end{figure}

In overcoming the challenges and achieving the multiscale model, uncertainties are introduced. 
While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the atomic coordinates are not exactly the same as that modeled by the many-electron schr\"{o}dinger equation.
So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
This is one source of uncertainty that have not been investigated.
But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
Secondly, state localization is not exactly a time dependent DFT process. 
But for amorphous OSCs used in this work, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
Lastly, the exchange-correlation potential in DFT do not have explicit formula and common practice is to use empirical functional, whose suitability is usually unknown for most molecules.

The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional in DFT will bring uncertainties to the multiscale model. 
In particular, different DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model.

@@

Most literature report the charge mobility in a steady state setting, where no electrodes are used and the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions. 
Over a long time period, the charge occupation on each molecule $\pi_i$ reach equilibrium, and the steady state diffusive velocity is calculated via:
\begin{equation}
    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} \vec{r}_{ij} = \mathbb{E}f(M_{\infty})
\end{equation}

Specifically, the focus will be placed on following questions: 
\begin{enumerate}
    \item How do DFT functionals change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
    \item How do DFT functionals change the charge mobility?
    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution?
    \item Can we estimate the range of the quantity of interest, given a confidence level?
\end{enumerate}

Calculation of $v_\text{ToF}$ or $v_\text{SS}$ commonly use kinetic Monte Carlo (KMC) to obtain multiple realizations of full charge dynamic trajectories 
or numerically solving the master equation. 
However, those two commonly used methods are not suitable for quantifying the uncertainty effect of multiscale model charge dynamics for the following reasons. 
Firstly, KMC produces random variables whose expectation is the charge mobility. The prior knowledge of the random variable distribution as well as the required KMC samples to achieve converged expectation is unknown. So this method itself pose further challenge for our uncertainty quantification. 
Secondly, the numerical solution of the master equation has stability and convergence issue, that is, a small integration time step is required to achieve stability and a long computational time to achieve convergence result. These aspects add additional difficulty for uncertainty quantification. 
Considering those aspects, the ToF $\tau$ and $v_\text{ToF}$ are obtained via a graph random walk method
\cite{chen_graph_2024}. Once the $v_\text{ToF}$ is calculated using this method, it is considered to be converged. 
Similarly, the steady state occupation $\pi_i$ will be calculated as the null-space of the transition matrix.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multiscale Model}
The multiscale model results in the charge dynamics becoming CTRW. When there in one charge carrier, each state in CTRW corresponds to the charge occupation in each molecule. The transition rates between the state, that is the rate for charge transfer rates between two molecules $i$ and $j$ is calculated as the Marcus rate:
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi R_{ij} k_\text{B}T}} \exp\left(-\frac{(E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - R_{ij})^2}{4R_{ij} k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation. The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated cyclic boundary conditions depending on the boundary condition. The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $R_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}). With the information about the molecular COMs and the rates, one can construct the graph $\mathbf{G}=(\mathbf{V}, \mathbf{W})$ on which the CTRW takes place. $\mathbf{V}$ is a set of nodes (molecules) and $\mathbf{W}: \omega_{ij}$ is the adjacency matrix. A rate is only considered between molecules $i$ and $j$ if their closest-contact distance is smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.

In the section, the components of the multiscale model will be introduced: molecule dynamics, calculation of reorganization energy, molecule energy, coupling element, $v_\text{SS}$ and $v_\text{ToF}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Molecule Dynamics Simulation}
In a material system of $N_a$ atoms with mass and position denoted by $m_i$ and $\vec{r}_i$ respectively, molecular dynamics (MD) models the evolution of the atomic coordinate using Newton's second law, which is written in Hamilton equation: 
\begin{equation}
    \begin{cases}
        \frac{d \vec{r}_i}{dt} = \frac{\partial H }{\partial \vec{p}_i} \\
        \frac{d \vec{p}_i}{dt} = -\frac{\partial H }{\partial \vec{r}_i}
    \end{cases}
    \label{eq:Hamilton}
\end{equation}
for $i=1,\cdots,N_a$, where the Hamiltonian $H$ reads:
\begin{equation}
    H=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})
    \label{eq:Hamilton2}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Electronic Structure Calculations} 
%Each molecule is an $N_\text{el}$-electron system, and in quantum mechanics, the probability of finding electrons in space is described by the electron wavefunction $\phi(\vec{r})$.
Effective single-electronic wave functions $\phi_l (\vec{r})$ and associated energies $\epsilon_l$ for a system with $N_\text{el}$ electrons are determined as solutions to the Kohn--Sham equations~\cite{kohn_self_1965}
%
\begin{equation}
    \left(-\frac{1}{2}\nabla^2_{\vec{r}} + v_\text{ext}(\vec{r}) + v_\text{H}[\rho](\vec{r}) + v_\text{XC}[\rho](\vec{r})\right) \phi_l(\vec{r}) =  \epsilon_l \phi_l (\vec{r}) ,
    \label{eq:KS2}
\end{equation}
%
where $v_\text{ext}$ in an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\vec{r})$, and $v_{XC}[\rho]$ the exchange-correlation functional containing explicit quantum-mechanical electron-electron interactions. The charge density is determined from the single-particle wave functions as $\rho(\vec{r})=\sum\limits_{l=1}^{N_\text{el}} \left\vert\phi_l(\vec{r})\right\vert^2$.

%
\begin{equation}
    U[\rho] = T_s[\rho] + \int \hat{V}_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]
    \label{eq:KS_model}
\end{equation}
%
where the electron density is , $T_s[\rho]$ is the kinetic energy depending on $\rho$,  $\hat{V}_\text{ext}$ is the external potential energy,  $\hat{V}_\text{H}[\rho]$ is the Hartree energy accounting for the Coulomb interaction, $\hat{V}_\text{XC}[\rho]$ is the exchange-correlation energy accounting for the difference between classical and quantum effect. The exact form of $\hat{V}_\text{XC}[\rho]$ is not known, in practice, this energy term is approximated by DFT functionals. In our work, different functionals are tested on BCP molecular system to check the effect of different functionals' impact on charge mobility. Different functionals have different ways to represent the exchange-correlation potentials, such as different level of HF exchange potential. 
Then PBE0 functional is used with varying HF component in the exchange-correlation potentials.

In practice, Equation \ref{eq:KS2} is solved iteratively, and the wave function is represented by a linear combination of basis functions call basic sets. 
In this work, the basic set def2-tzvp \cite{weigend_accurate_2006} is used. The DFT computation is performed by VOTCA \cite{Baumeier2011} which internally calls ORCA software.

The internal energy $U_i$ of molecule $i$ depends on the charge states and atomic coordinate (also called geometry) of the molecule. 
The optimized geometry of a molecule refers to the atomic coordinates that minimize $U_i$.
Here we use $U_i^\text{xX}$ to denote the internal energy of molecule $i$ at charge state x in the optimized geometry X. Neutral and charge states are represented as x=n and c, respectively. Similarly, optimized neutral molecular geometry and optimized charge molecular geometry are represented by X=N and C, respectively.

The reorganization energy $R_{ij}$ from molecule $i$ to molecule $j$ is given as:
\begin{equation}
    R_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
\end{equation}
where $U_i^\text{nC}$ is the internal energy of the neutral molecule $i$ in optimized geometry of charged molecule, calculated from Equation \ref{eq:KS_model}. 
And $U_i^\text{nN}$ the internal energy of the neutral molecule $i$ in optimized geometry of neutral molecule. Similarly, $U_j^\text{cN}, U_j^\text{cC}$ are defined in this way.
When charge carriers are holes, a charged molecule has one electron less compared to a neutral molecule. 
For the BCP device, we obtain $R_{ij}=0.50$ eV since this is only one type of molecule.

In a single-component system where internal energy difference of molecule $i$ and $j$ is equal, the energy difference $E_{ij}$ is calculated by:
\begin{equation}
    E_{ij} = E_i - E_j
    \label{eq:siteE}
\end{equation}
where $E_i = E_i^\text{c} - E_i^\text{n},E_j = E_j^\text{c} - E_j^\text{n}$ are the molecule energies, the superscript represents charge state or neutral state molecule as mentioned above. And $E_i^\text{n} = E_i^\text{n,el} + E_i^\text{n,induce}$ considers the electrostatic energy as well as the energy from the induced dipole moment.
In multiscale model, $E_i^\text{n} = E_i^\text{n,el} + E_i^\text{n,induce}$ is calculated iteratively from the Thole Model as detailed in \cite{thole_molecular_1981}.
% instead of using a dielectric constant as been done in the bulk system at macroscopic scale. 
Specifically, the first step is to calculate the induced dipole at atom $a_i$ by electrostatic field. This induced dipole will change the dipole moment at all other atoms $b_j \neq a_i$. Then repeat this step and recalculate the induced dipole at atom $a_i$, followed by induced dipoles at all other atoms $b_j$. This process is repeated until the induced dipole converge to a fix value. 
In short summary, the $E_i$ is a function of all individual atoms' charges $q$ and induced dipole $\mu$: $E_i^\text{n,el} + E_i^\text{n,induce} = \sum\limits_{a_i} f(q_{a_i}, \mu_{a_i})$ where $a_i$ goes over all the atoms in the system. 
The calculation of $E_i^\text{c} = E_i^\text{c,el} + E_i^\text{c,induce}$ uses similar iteratively process as $E_i^\text{n}$.
The molecule energies and their distribution are shown in the appendix.

%%%%%%%
The coupling element $J_{ij}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
\begin{equation}
    J_{ij} = \frac{ J^0_{ij}- \frac{1}{2}(e_i+e_j) S_{ij} }{ 1- S_{ij}^2 }
    \label{equ:JAB}
\end{equation}
where $J^0_{ij} = \langle \phi^\text{HOMO}_i | \hat{H} | \phi^\text{HOMO}_j \rangle $, $e_i = \langle \phi^\text{HOMO}_i | \hat{H} | \phi^\text{HOMO}_i \rangle $, $e_j = \langle \phi^\text{HOMO}_j | \hat{H} | \phi^\text{HOMO}_j \rangle $, and $S_{ij}=\langle \phi^\text{HOMO}_i | \phi^\text{HOMO}_j \rangle $ with bra-ket notation.
For hole-transporting OSCs system such as the BCP used in this work, $\phi^\text{HOMO}_i$ is the HOMO electron wave function of molecule $i$. 
The Kohn-Sham Hamiltonian is $\hat{H} = -\frac{1}{2}\nabla^2_{\vec{r}} + \hat{V}_\text{ext} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]$. 
A single molecule is called a monomer, and a pair of two molecules is called a dimer.

Denote $\phi^\text{HOMO}_\text{D}$ as the HOMO electron wave function of the dimer,  $J^0_{ij}$ can be calculated via:
$
    J^0_{ij} = \mathbf{p}^i \text{diag}(\mathcal{E}) \mathbf{p}^j
$, 
where the vector $\mathbf{p}^i = \langle \phi_i^\text{HOMO} | \phi^\text{HOMO}_\text{D} \rangle$ and $\mathbf{p}^j = \langle \phi_j^\text{HOMO} | \phi_\text{D}^\text{HOMO} \rangle$ are called the projections of the monomer orbitals $\phi_i^\text{HOMO}, \phi_j^\text{HOMO}$ onto the dimer orbitals $\phi^\text{HOMO}_\text{D}$. And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting eigenvalues of the basis function of $\phi_\text{D}^\text{HOMO}$. The molecular coupling element distribution is shown in the appendix.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Time-of-flight Calculation}
The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the nodes represent molecules and the edge weights $\omega_{ij}$ represent the Marcus rate from molecule $i$ to molecule $j$. 
The charge dynamics are modeled as a continuous-time random walk on this graph. In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.

In CTRW the ToF is calculated as the expected hitting time of a continuous time Markov chain.

For a system with $N$ molecules and one charge carriers, there are $N$ possible occupation states. A state is called the Source state if one of the Source molecule is occupied, and a Sink state is the one when one of the Sink molecule is occupied.

The transition rates between the states defines the adjacency matrix $\mathbf{W}:\omega_{ij}$.
According to such connectivity between the molecules, the transition rates $\mathbf{W}_{ij}$ from state $i$ to $j$ is:
\begin{equation}\label{eq:transition_rates}
	\mathbf{W}_{ij} =
	\begin{cases}
	     0			&  i \text{ is not connected to } j,\\
         \omega_{ij}   &  i \text{ is connected to } j,
	\end{cases}
\end{equation}

Then the transition probability from state $i$ to $j$ is $p_{ij} = \mathbf{W}_{ij}/D_i$ where $D_i := \sum_{j} \mathbf{W}_{ij}$.
And the expected time from state $i$ to reach the Sink state $\tau_i$ is calculated via: 
\begin{equation}\label{eq:hitting_time}
	\tau_i = \begin{cases}
		\frac{1}{D_i} + \sum_{j \ne i} p_{ij} \tau_{j} &\text{if $i$ is not a sink state},\\
		0 &\text{else.} 
	\end{cases}
\end{equation}

To account for all possible starting nodes of the carriers, all Source states must be considered. The random walk process can be modeled as a parallel electric network of capacitors \cite{doyle_random_2000}. Accordingly, the ToF is evaluated using the harmonic mean:
\begin{equation} 
\tau = N_\text{source} \left[\sum_{i \in \text{Source}} (\tau_i)^{-1}\right]^{-1},
\label{eq:ToF}
\end{equation}
where $N_\text{source}$ is the number of Source states.
